\newpage
\section{Issues Faced}
\subsection{Server Crash: macOS Not Supporting Realtime Monitoring}
\begin{itemize}
    \item For the File Integrity Module (FIM), we were opting for realtime monitoring for both Windows and Linux.
    \item But this configuration was not working on macOS. Later, we found out that macOS does not support realtime monitoring to begin with.
    \item We had to set a monitoring frequency then. Naively, we chose 1 second.
    \item Because of such frequent logging, the server could not take the load and suffered a crash.
    \item Later, we changed the frequency to 1 minute and restarted the server. Things started working nicely afterwards.
\end{itemize} 

\subsection{Random Authentication Error on Server}
\begin{itemize}
    \item Strangely enough, at times, we could not login to Wazuh dashboard with appropriate username and passwords. It just said, incorrect username or password.
    \item We examined the \texttt{wazuh-install-files/wazuh-passwords.txt} and saw our credentials were alright.
    \item Even more strangely, everytime the problem got fixed by a restart of the server.
\end{itemize}

\subsection{Source Code Compilation Challenges}
\begin{itemize}
    \item Documentation and detailed instructions are pretty scant. 
    \item The exact release tag of the repository needs to be checked out for the source code to compile. The master branch doesn't always compile with the officially provided scripts.
    \item The OpenSearch, OpenSearch Dashboard and Wazuh versions need to be compatible in order for \texttt{dev.sh} script to work. However, compatible versions aren't documented anywhere.
\end{itemize}
\section{Reference}
\begin{itemize}
    \item \href{https://documentation.wazuh.com}{The Official Wazuh Documentation}
    \item \href{https://github.com/wazuh}{Wazuh GitHub Repositories}
\end{itemize}